\includegraphics*[width=0.4\textwidth]{hpi_logo_2017.eps}\\ \vspace{24pt} Genetic Doodle Jump

### 2018-03-20 paper/paper.tex
abstract

% Koma-Script Basisklasse
\documentclass[a4paper,12pt,pagesize,headsepline,bibtotoc,titlepage]{scrartcl}

@@

\begin{document}
\maketitle
\tableofcontents
\newpage

@@

\section{Doodle Jump}
\subsection{Original game}
The video game Doodle Jump is developed for mobile devices by Lima Sky\footnote{\url{http://www.limasky.com/}}. The player --- the so called \quot{doodler} --- has to jump on platforms in order to get a higher score. There are four different types of platforms:
\begin{enumerate}
    \item Regular ones, which neither move nor break
    \item Horizontally moving platforms
    \item Vertically moving platforms
    \item Vanishable ones, which disappear after jumping on it once
    \item Breaking platforms, where the doodler can't jump on
\end{enumerate}
The platforms are pseudo randomly located on the map. Pseudo randomly located means, that there will always be at least one platform, which is reachable from the previous one and non-breakable (See Fig. \ref{abb:doodlejumpgame}). In other words, there is always a way to reach an infinite score. However, the higher the achieved score, the more difficult the game becomes. The difficulty is reached via higher distances between the platforms and the increased usage of moving and vanishable platforms.

@@

\section{User Interface}

>>>>

% Koma-Script Basisklasse
\documentclass[a4paper,12pt,pagesize,headsepline,bibtotoc,titlepage,abstracton]{scrartcl}

@@

\begin{document}
\maketitle
\tableofcontents

\newpage

\begin{abstract}
Teaching an AI to play a simple game has become an interesting research topic in the last couple of years. Games usually have a wide range of possible parameters to tune. Often times, simple neural networks can meet all the requirements and perform well. However, training the net often takes many hours or a few days. The training time can be reduced tremendously by using a neural nets in combination with a genetic algorith. In this paper we present how we applied a deep genetic algorithm on the game \quot{Doodle Jump}. We especially pay attention to the configuration of the genetic algorithm, describe the undertaken changes and show, which influence they have on the performance.
\vskip 0.7cm
\noindent \textbf{Keywords.} Deep Learning, Genetic Algorithm, Artificial Intelligence, Games

\newpage

@@

\section{Doodle Jump}
\subsection{Original game}

The video game Doodle Jump is developed for mobile devices by Lima Sky\footnote{\url{http://www.limasky.com/}}. The player --- the so called \quot{doodler} --- has to jump on platforms in order to get a higher score. There are four different types of platforms:
\begin{enumerate}
    \item Regular ones, which neither move nor break
    \item Horizontally moving platforms
    \item Vertically moving platforms
    \item Vanishable ones, which disappear after jumping on it once
    \item Breaking platforms, where the doodler can't jump on
\end{enumerate}
The platforms are pseudo randomly located on the map. Pseudo randomly located means, that there will always be at least one platform, which is reachable from the previous one and non-breakable (See Fig. \ref{abb:doodlejumpgame}). In other words, there is always a way to reach an infinite score. However, the higher the achieved score, the more difficult the game becomes. The difficulty is reached via higher distances between the platforms and the increased usage of moving and vanishable platforms.

@@

Since we do not want to perform the deep learning part on a mobile devices or within an emulator, we decided to use an implementation, which runs in a browser. We are using \quot{HTML5 Doodle Jump} by ntcnet83\footnote{\url{https://github.com/ntcnet83/html5-doodle-jump}}, which we found on github\footnote{\url{https://github.com/}}. This custom version of the is written in HTML5 and JavaScript.

MUCH TODO HERE!
\section{User Interface}
